%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Thin Formal Letter
% LaTeX Template
% Version 1.11 (8/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% WikiBooks (http://en.wikibooks.org/wiki/LaTeX/Letters)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{letter}

% Adjust margins for aesthetics
\addtolength{\voffset}{-0.5in}
\addtolength{\hoffset}{-0.3in}
\addtolength{\textheight}{2cm}

%\longindentation=0pt % Un-commenting this line will push the closing "Sincerely," to the left of the page

%----------------------------------------------------------------------------------------
%	YOUR NAME & ADDRESS SECTION
%----------------------------------------------------------------------------------------

\signature{WANG Hailong} % Your name for the signature at the bottom

\address{Room 608, Building A, \\ Tairan Trade \& Industry Park, \\ Tian'an Digital Town \\ Shen Zhen, Guang Dong \\ +86 186-7677-1962} % Your address and phone number

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	ADDRESSEE SECTION
%----------------------------------------------------------------------------------------

\begin{letter}{CTO \\ Shenzhen Fecocyan Science Technology Co., Ltd \\ ShenZhen, GuangDong, China} % Name/title of the addressee

%----------------------------------------------------------------------------------------
%	LETTER CONTENT SECTION
%----------------------------------------------------------------------------------------

\opening{\textbf{Dear Sir or Madam,}}
 
As his superior and colleague, I highly recommend Mr. Qiao Wang to with great confidence and enthusiasm. I believe his solid professional background in computer science and algorithm makes him an ideal candidate for your master program.

Mr. Qiao Wang joined the company about a year ago when I served as the CTO of the company. As I first reviewed his program submitted in SVN, I was really impressed by his clean code, clear logic and solid programming skill. I was also surprised with his efficiency. At that time, we had a program which was implemented by another company. However, the project was progressing at a slow pace and had been prolonged for two months. Then I designated him as the manager of the program. He spent only one week in finishing the job. From then on, he was tagged as efficient and swift in our company.

As days went on, he had directed several other projects, which made me know him better. 	He is not afraid of challenging new areas, even though it is not his field. For instance, our server once could not work well when it was overwhelmed by a large number of visitors. It was he who had never touched server programming before that set out to learn the required knowledge and designed an improved migratory dynamic load-balancing algorithm according to the conception of sender-table and receiver-table. Finally the server was well improved and worked better. It revealed me his enthusiasm for technology.

Most importantly, he is very motivated and never gives up. Every time he bumps into questions, he asks the experienced for direction and grasp all the details through others’ help. For example, there’s a product of our company that frequently restarts abnormally. It bothered us for a long time but no one could find what was going wrong. When Qiao was tasked by the problem, he kept working on it for ten days, caught unusual signals, and finally solved it. Wang is not only of perseverance but also of curiosity about knowledge, he also attended regular technology seminars to update his mind.

Although it would be a pity for our company to see him leave, I believe his postgraduate study, if he would be admitted, can further improve his professional capability in the future, which would be an even greater contribution to our company. Thus I completely support his desire and aspiration to enroll in the prestigious master program in your department and I would like to offer my highest recommendation. If you admit his application, I ensure that it shall be not only a blessing for him and his academic and professional career but also a gift for your department. Therefore, I sincerely suggest you to take his application. Should you have any questions, please do not hesitate to contact me at: wanghailong@18.net

\vspace{2\parskip} % Extra whitespace for aesthetics
\closing{Sincerely,}
\vspace{2\parskip} % Extra whitespace for aesthetics


%----------------------------------------------------------------------------------------

\end{letter}
 
\end{document}